Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/survey.tex
merge

\begin{figure}
\begin{center}
%\fbox{\parbox{6cm}{
%This is a figure with a caption.}}
\includegraphics[scale=0.32]{figures/vulture.png} 
\begin{tabular}{lp{6cm}}
object id & linked region descriptions\\
\hline
3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
2385747 & small white beak of \textbf{bird}\\
2681429 & a semi \textbf{long beak}\\  
2346210 & a black and gray \textbf{vulture}\\
 \end{tabular}
\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
\label{fig:bird}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
%\fbox{\parbox{6cm}{
%This is a figure with a caption.}}
\includegraphics[scale=0.32]{figures/vulture.png} 
\begin{tabular}{lp{6cm}}
object id & linked region descriptions\\
\hline
3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
%2385747 & small white beak of \textbf{bird}\\
2681429 & a semi \textbf{long beak}\\  
2346210 & a black and gray \textbf{vulture}\\
 \end{tabular}
\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
\label{fig:bird}
\end{center}
\end{figure}
